### 2021-09-10 figure2.tex
home from trip
Installing on new alishan

% Created by tikzDevice version 0.12.3 on 2020-05-07 17:13:04
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.88,126.52) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.38,123.50) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38,126.52) --
	( 76.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38,126.52) --
	( 76.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38,126.52) --
	( 76.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88,228.77) --
	(120.88,228.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88,228.77) --
	(120.88, 65.26);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88, 65.26) --
	(120.88, 65.26);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38,154.56) --
	(165.38,154.56);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38,154.56) --
	(165.38,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38,104.90) --
	(165.38,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88,164.33) --
	(209.88,164.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88,164.33) --
	(209.88, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88, 76.82) --
	(209.88, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38,252.55) --
	(254.38,252.55);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38,252.55) --
	(254.38, 51.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38, 51.71) --
	(254.38, 51.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 76.38, 28.62) {none};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (120.88, 28.62) {$\mu_r$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (165.38, 28.62) {$\mu_G$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (209.88, 28.62) {$\mu_\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (254.38, 28.62) {all};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-09-10 14:27:21
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.38,126.52) circle (  5.71);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.88,123.50) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38,126.52) --
	(254.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38,126.52) --
	(254.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (254.38,126.52) --
	(254.38,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38,228.77) --
	(165.38,228.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38,228.77) --
	(165.38, 65.26);

\path[draw=drawColor,line width= 2.3pt,line join=round] (165.38, 65.26) --
	(165.38, 65.26);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88,154.56) --
	(120.88,154.56);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88,154.56) --
	(120.88,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (120.88,104.90) --
	(120.88,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38,164.33) --
	( 76.38,164.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38,164.33) --
	( 76.38, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] ( 76.38, 76.82) --
	( 76.38, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88,252.55) --
	(209.88,252.55);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88,252.55) --
	(209.88, 51.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (209.88, 51.71) --
	(209.88, 51.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at ( 76.38, 28.62) {$\mu_\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (120.88, 28.62) {$\mu_G$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (165.38, 28.62) {$\mu_r$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (209.88, 28.62) {all};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (254.38, 28.62) {none};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

### 2021-09-10 propagate_pix.tex
home from trip
good night
Installing on new alishan

% Created by tikzDevice version 0.12.3 on 2020-05-07 18:04:06
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (446.17,204.36) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59,417.54) --
	(187.59,417.54);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59,417.54) --
	(187.59, 86.40);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59, 86.40) --
	(187.59, 86.40);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17,465.70) --
	(446.17,465.70);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17,465.70) --
	(446.17, 58.97);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17, 58.97) --
	(446.17, 58.97);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (187.59, 28.62) {$\mu_r$};

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-09-10 14:27:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (446.17,210.47) circle (  5.71);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (359.98,204.36) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17,210.47) --
	(446.17,210.47);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17,210.47) --
	(446.17,210.47);

\path[draw=drawColor,line width= 2.3pt,line join=round] (446.17,210.47) --
	(446.17,210.47);

\path[draw=drawColor,line width= 2.3pt,line join=round] (273.79,417.54) --
	(273.79,417.54);

\path[draw=drawColor,line width= 2.3pt,line join=round] (273.79,417.54) --
	(273.79, 86.40);

\path[draw=drawColor,line width= 2.3pt,line join=round] (273.79, 86.40) --
	(273.79, 86.40);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59,267.25) --
	(187.59,267.25);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59,267.25) --
	(187.59,166.69);

\path[draw=drawColor,line width= 2.3pt,line join=round] (187.59,166.69) --
	(187.59,166.69);

\path[draw=drawColor,line width= 2.3pt,line join=round] (101.40,287.03) --
	(101.40,287.03);

\path[draw=drawColor,line width= 2.3pt,line join=round] (101.40,287.03) --
	(101.40,109.81);

\path[draw=drawColor,line width= 2.3pt,line join=round] (101.40,109.81) --
	(101.40,109.81);

\path[draw=drawColor,line width= 2.3pt,line join=round] (359.98,465.70) --
	(359.98,465.70);

\path[draw=drawColor,line width= 2.3pt,line join=round] (359.98,465.70) --
	(359.98, 58.97);

\path[draw=drawColor,line width= 2.3pt,line join=round] (359.98, 58.97) --
	(359.98, 58.97);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (101.40, 28.62) {$\mu_\kappa$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (187.59, 28.62) {$\mu_G$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (273.79, 28.62) {$\mu_r$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (359.98, 28.62) {all};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.28] at (446.17, 28.62) {none};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}
